---
title: "data.table"
subtitle: "Extension of `data.frame`"
author: "Mario Annau"
date: "12/12/2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(microbenchmark)
source("functions.R")
```

## Introduction

- Created by Matt Dowle in 
- Most downloaded package according to ...
- High performance version of data.frame

## Why is data.table fast?

- Hashed indices


## data.table basics 

Video from UseR! 2014: https://www.youtube.com/watch?v=qLrdYhizEMg

General syntax:

```{r, echo=TRUE, eval=FALSE}
library(data.table)
DT[i, j, by]
```

- i: On which rows (WHERE)
- j: What to do (SELECT)
- by: Grouped by what? (GROUP BY)

## Problem 1: Calculate USD cross rates on Poloniex

1.1. Aggregate all BTC denominated quotes to minute bars
1.2. (Roll-)Join all BTC quotes to one table
1.3. Calculate implied USD Cross rates using USDT_BTC
1.4. Compare USD Cross rates with existing ones and see if there are discrepancies/arbitrage opportunities

## Problem 1: Calculate USD cross rates on Poloniex

The code is basically as follows:

```{r, eval = FALSE, echo=TRUE}
dat <- data.table(dat)
dat[, Index := index]
setkey(dat, Date) # do the ordering implicitly
setkey(dat, Index)

dat[, .(Open = data.table::first(Price), 
       High = max(Price), 
       Low = min(Price), 
       Close = data.table::last(Price), 
       Volume = sum(Volume)), by = Index]
```


```{r, cache=TRUE, echo=FALSE, eval=TRUE, results='asis'}
#poloniex <- h5file("data/poloniex.h5", mode = "r")
#allquotes <- list.groups(poloniex)
#quotes.btc <- grep("BTC_", allquotes, value = TRUE, fixed = TRUE)

btcxrp <- load_data("data/poloniex.h5", "BTC_XRP", folder = "POLONIEX")[[1]]
index <- calc_index(btcxrp)
mb <- microbenchmark(
  agg_ohcl_base_r(btcxrp, index),
  agg_ohcl_dplyr(btcxrp, index),
  agg_ohcl_data_table(btcxrp, index), 
  times = 1)
knitr::kable(mb)
```



# data.frame(sort(sapply(allquotes, function(g) poloniex[[sprintf("%s/trades", g)]]$dims[1]), decreasing = TRUE))
# sort(sapply(allquotes, function(g) poloniex[[sprintf("%s/trades", g)]]$dims[1]), decreasing = TRUE)
quotes.usd <- grep("USDT_", allquotes, value = TRUE, fixed = TRUE)

ccy.usd <- sapply(strsplit(quotes.usd, "_"), function(x) x[2])
ccy.btc <- sapply(strsplit(quotes.btc, "_"), function(x) x[2])


kraken <- h5file("data/kraken.h5", mode = "r")
```










## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

